\documentclass[letter]{res}

\setlength{\textheight}{10.5in}
%\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[dvipsnames]{xcolor}
%\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=17mm,
 bottom=17mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\usepackage{amsmath}
\setlist{nolistsep}

\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}
%\usepackage[colorlinks=true,linkcolor=Bittersweet,urlcolor=Bittersweet]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{multicol}



\usepackage{comment}

\begin{document}

\name{\textcolor{Bittersweet}{SAROJ PRASAD CHHATOI}\\
}
\address{+33-749254998}
\address{
  \texttt{spchhatoi@laas.fr}\\ 
  \texttt{chhatoisaroj@gmail.com}
}
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}


\section{\textcolor{Bittersweet}{Education}}
 \begin{itemize}
 \item {\sl \textbf{LAAS-CNRS, Toulouse, France}
} \\ Automatic Control \hfill  Feb 2023 - March 2026\\
\textit{Doctoral Candidate\\ Supervisors: Aneel Tanwani, Didier Henrion}
  \item {\sl \textbf{University of California, Los Angeles}
}\\ Noncommutative Optimal Transport \hfill Mar. 2025 - Jun. 2025 \\
\textit{Visiting Graduate Researcher } 
 \item {\sl \textbf{Institute Of Mathematical Sciences, Chennai}
} \\ Physics \hfill  Aug. 2017 - Jul. 2020\\
\textit{Master of Science, Junior Research Fellow }
 
 \item {\sl \textbf{Indian Institute Of Technology Jodhpur}
}\\ Systems Engineering  with Specialization in Electrical Engineering \hfill Jun. 2013 - May 2017 \\
\textit{Bachelor of Technology } 
   
 \end{itemize}
   \vspace{-2mm}

\section{\textcolor{Bittersweet}{Journal Articles}}
\href{https://www.sciencedirect.com/science/article/pii/S0005109825002961}{\textbf{Evolution of Measures in Nonsmooth Dynamical Systems}} \newline  
{\sl Co-authors: Aneel Tanwani, Didier Henrion \\
Automatica, (Vol. 179, art. 112402, 2025)
}

\href{https://www.aimsciences.org/article/doi/10.3934/dcds.2025051}{\textbf{Optimizing Quasi-Dissipative Evolution Equations with the Moment-SOS Hierarchy}}\newline 
{\sl Co-authors: Swann Marx, Nicolas Seguin, Didier Henrion \\
Discrete and Continuous Dynamical Systems – Series A (DCDS-A)}(Vol. 45, no. 11, 2025)

\href{https://link.springer.com/article/10.1007/s11590-026-02285-x}{\textbf{Approximating the Order-2 Quantum Wasserstein Distance Using the Moment–SOS Hierarchy}} \newline
{\sl Co-author: Victor Magron}\newline
Optimization Letters, (Vol. 20, Issue 1, 2026)


\href{https://doi.org/10.1109/TRO.2023.3288837}{\textbf{Optimal Control For Articulated Soft Robots}}\newline
{\sl Co-authors: Michele Pierallini, Franco Angelini, Carlos Mastalli, Manolo Garabini \\
IEEE Transactions on Robotics (Vol. 39, No. 5, Oct. 2023)}

\href{https://doi.org/10.1109/TRO.2023.3262186}{\textbf{Inverse Dynamics based Model Predictive Control via Nullspace Resolution}}\newline 
{\sl Co-authors: Carlos Mastalli, Thomas Corbères, Steve Tonneau, Sethu Vijayakumar\\
IEEE Transactions on Robotics (Vol. 39, No. 4, Aug. 2023)}







\section{\textcolor{Bittersweet}{Unpublished Articles and Preprints}}

\href{https://spykspeigel.github.io/OCNSD/OCNsd.pdf}{\textbf{Optimal Control of State Constrained Systems via Measure Relaxations and Polynomial Optimization}}\newline 
\textsl{(Under review, with Aneel Tanwani and Didier Henrion)}

\href{https://hal.science/hal-05487303}{\textbf{A Gaussian surrogate of partially observed stochastic processes using Wasserstein metric}} \newline
\textsl{(Under review, with Ibrahim Ramadan and Aneel Tanwani)}

\href{https://www.ipam.ucla.edu/reports/white-paper-non-commutative-optimal-transport}{\textbf{Quantum Gradient Structures from Large Deviations and Quantum Thermodynamics}}\newline
\textsl{White paper, IPAM Noncommutative Optimal Transport long program (co-author, with participants).}



\href{https://arxiv.org/abs/2503.23815}{\textbf{Shannon‐ and von Neumann‐entropy regularizations of linear and semidefinite programs}}\newline
{\sl (with  Jean B.~Lasserre)} 
    


\section{\textcolor{Bittersweet}{Conference Articles}}
\href{https://doi.org/10.1109/CDC56724.2024.10885896}{\textbf{Optimal Control of Nonsmooth Dynamical Systems using Measure Relaxations}}\newline 
- {\sl IEEE Conference on Decision and Control 2024, Milan (\url{ https://hal.science/hal-04701838})\\ Co-authors: Aneel Tanwani, Didier Henrion
}


\href{https://doi.org/10.5281/zenodo.14731033}{\textbf{Articulated Soft Robots: A Feasibility Driven Control Approach}} \newline
- {\sl I-RIM Conference 2024, Rome (DOI: 10.5281/zenodo.14731033)\\
Co-authors: Davide De Benedittis, Michele Pierallini, Franco Angelini, Carlos Mastalli, and Manolo
Garabini}

%\section{\textcolor{Bittersweet}{Master's Thesis}}
%\href{https://github.com/spykspeigel/Master_thesis/blob/master/thesis_1.pdf}{\textbf{Aspects of S-Matrix Theory in Quantum Field Theory}} \newline - {\sl Supervisor: Dr. V.S. Nemani}
% \begin{itemize} \item {
% In this report, we  explored  aspects of S-matrix program like the Froissart-Gribov theorem, the double discontinuity theorem, Froissart theorem, properties of regge poles and how these concepts arise in non-relativistic quantum mechanics.}
% \end{itemize}
  \vspace{-2mm}


\section{\textcolor{Bittersweet}{Work Experiences}}
      
\textbf{Centro E. Piaggio, University of Pisa, Italy} \newline - {\sl Research Fellow}\hfill Jul. 2021 - Jan. 2023 \\
 \vspace{-2mm}
\begin{itemize}\item Optimal planning and control of legged robots. 
\end{itemize}
  \vspace{-2mm}
  

  
  \textbf{Flytbase Inc., Pune, India} \newline - {\sl Robotics Engineer}\hfill Apr. 2021 - Jun. 2021 \\
 \vspace{-2mm}
\begin{itemize}\item Part of the precision landing team.
\end{itemize}
  \vspace{-2mm}
    
  
  
  \textbf{HiTech Robotic Systems Ltd., Gurgaon, India} \newline - {\sl Senior Research Engineer}\hfill Dec. 2020 - Apr. 2021 \\
 \vspace{-2mm}
\begin{itemize}\item Responsible for improving the existing control and motion planning architecture.
\end{itemize}
  \vspace{-2mm}
  

  
   \textbf{Robotics Research Center, International Institute of Information Technology, Hyderabad, India} \newline - {\sl Research Intern under Dr. K. Madhava Krishna}\hfill Mar. 2020 - Nov. 2020 \\
 \vspace{-3mm}
 \begin{itemize}
  \item {  Worked on lab's funded project with Rockwell Collins Aerospace on non-holonomic multiagent motion planning frameworks.
  }
    
 %   \end{itemize}
  \vspace{-2mm}
    \end{itemize}
   
\section{\textcolor{Bittersweet}{Workshops and Graduate Courses}}
\begin{itemize}
    \item Oberwolfach workshop on ``Polynomial Optimization for Nonlinear Dynamics" (Aug. 2024)
    \item Stochastic Calculus (Graduate Course, IMT Toulouse, Instructor: Serge Cohen)(Sept. 2024 - Nov. 2024)
    \item Elliptic PDEs and Evolution equations (Graduate Course, IMT Toulouse, Instructor: Mihai Maris)(Sept. 2024 - Nov. 2024)
    \item Introduction to Optimal Transport (Graduate Course, IMT Toulouse, Instructor: Jerome Betrand)(Sept. 2024 - Nov. 2024)
    \item Convergence of Probability measures (Graduate Course, IMT Toulouse, instructor: Clement Pellegrini)(Sept. 2023 - Nov. 2023)
    \item Stochastic processes (Graduate Course, IMT Toulouse, Instructor: Francois Chapon)(Jan. 2024 - Apr. 2024)
    \item Summer school on Applied Harmonic Analysis and Machine learning, Genoa (Aug. 2024)
    \item Summer school on Nonsmooth dynamical systems, Paris (Apr. 2023)
\end{itemize}

\section{\textcolor{Bittersweet}{Awards}}
\begin{itemize}
    \item \textbf{Graduate Fellow}, Institute for Pure and Applied Mathematics, University of Los Angeles, California (Mar. 2025 - Jun. 2025)
    \item \textbf{Leibniz graduate fellow}, Oberwolfach Workshop on ``Polynomial Optimization for Nonlinear Dynamics: Theory, Algorithms, and Applications", Mathematisches Forschungsinstitut Oberwolfach (Aug. 2024)
    \item \textbf{Student Travel and Workshop Support} for IEEE Conference on Decisions and Control 2024
    \item \textbf{Best poster presentation} at IEEE-RAS TC Model-Based Optimization  for Robotics 2023  ``Inverse Dynamics MPC via Nullspace Resolution"
    \item  \textbf{Finalists for best paper award} at IEEE-ICRA TC Model Based Optimization for Robotics 2024 ``Inverse Dynamics MPC via Nullspace Resolution"
\end{itemize}

\section{\textcolor{Bittersweet}{Skills}}
{\sl Languages:} C,~C++,~Julia,~Python,~MATLAB,~Fortran,~Mathematica \\
{\sl Tools/Platforms:} ROS,~Gazebo,~Git,~\LaTeX \\
{\sl Libraries/Frameworks:} NumPy,~SciPy,~scikit-learn,~TensorFlow,~PyTorch,~GloptiPoly \\
{\sl Certifications:} Coursera (2020): Intro to TensorFlow for AI/ML/DL (PEJJL4QPWX9K), CNNs in TensorFlow (Q5AXUBEQ835C), Sample-based Learning Methods (GPLL62V6R36N)

\section{\textcolor{Bittersweet}{Referees}}
\begin{itemize}
    \item \textbf{Tryphon T. Georgiou} \hfill \texttt{tryphon@uci.edu}
    \item \textbf{Marius Junge} \hfill \texttt{mjunge@illinois.edu}
    \item \textbf{Didier Henrion} (Supervisor) \hfill \texttt{henrion@laas.fr}
    \item \textbf{Aneel Tanwani} (Supervisor) \hfill \texttt{tanwani@laas.fr}
\end{itemize}

\end{resume}
\end{document}